Covariate analysis of HBCC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (DLPFC with CQN and SVA normlaisation)

### 2017-08-08 code/Rmd/HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_SVA.Rmd
Minor bug fix

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'CMC_ACC_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = File('CMC_ACC_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
annotations(COV_OBJ) = annotations(CODE)
annotations(COV_OBJ)$dataSubType = 'covariates'
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('CMC_ACC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
annotations(COUNT_OBJ) = annotations(CODE)
annotations(COUNT_OBJ)$dataSubType = 'filteredCounts'
COUNT_OBJ = synStore(COUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store filtered counts
NEW.COUNTS %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_nCounts.tsv', sep = '\t', row.names=F, quote=F)
NCOUNT_OBJ = File('CMC_ACC_DLPFC_nCounts.tsv', name = 'Counts (estimated)', parentId = CODE$properties$id)
annotations(NCOUNT_OBJ) = annotations(CODE)
annotations(NCOUNT_OBJ)$dataSubType = 'estimatedCounts'
NCOUNT_OBJ = synStore(NCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store logCPM
CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('CMC_ACC_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
annotations(LCOUNT_OBJ) = annotations(CODE)
annotations(LCOUNT_OBJ)$dataSubType = 'filteredLCPM'
LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_offset.tsv', sep = '\t', row.names=F, quote=F)
OFFSET_OBJ = File('CMC_ACC_DLPFC_offset.tsv', name = 'Gene length and GC content offset', parentId = CODE$properties$id)
annotations(OFFSET_OBJ) = annotations(CODE)
annotations(OFFSET_OBJ)$dataSubType = 'offset'
OFFSET_OBJ = synStore(OFFSET_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store design matrix
DM1$design %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'CMC_ACC_DLPFC_Design.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = File('CMC_ACC_DLPFC_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
annotations(DM_OBJ) = annotations(CODE)
annotations(DM_OBJ)$dataSubType = 'designMatrix'
DM_OBJ = synStore(DM_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store design matrix
SURR.VAR %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'CMC_ACC_DLPFC_SurrVar.tsv', sep = '\t', row.names=F, quote=F)
SURR.VAR_OBJ = File('CMC_ACC_DLPFC_SurrVar.tsv', name = 'Surrogate Variables', parentId = CODE$properties$id)
annotations(SURR.VAR_OBJ) = annotations(CODE)
annotations(SURR.VAR_OBJ)$dataSubType = 'surrogateVariable'
SURR.VAR_OBJ = synStore(SURR.VAR_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store residual gene expression for network analysis
RESIDUAL.SVA.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'CMC_ACC_DLPFC_eqtlResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
eEXP_OBJ = File('CMC_ACC_DLPFC_eqtlResidualExpression.tsv', 
                name = 'Normalised, covariates removed residual expression (for eQTL analysis)', 
                parentId = CODE$properties$id)
annotations(eEXP_OBJ) = annotations(CODE)
annotations(eEXP_OBJ)$dataSubType = 'residualGeneExpForNetAnlz'
eEXP_OBJ = synStore(eEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

>>>>

# Store covariates
COVARIATES = rownameToFirstColumn(COVARIATES, 'SampleID')
write.table(COVARIATES, file = 'HBCC_DLPFC_Covariates.tsv', sep = '\t', row.names=F, quote=F)
COV_OBJ = File('HBCC_DLPFC_Covariates.tsv', name = 'Covariates', parentId = CODE$properties$id)
annotations(COV_OBJ) = annotations(CODE)
annotations(COV_OBJ)$dataSubType = 'covariates'
COV_OBJ = synStore(COV_OBJ, used = ALL_USED_IDs, activityName = activityName, 
                      executed = thisFile, activityDescription = activityDescription)

# Store filtered counts
PROCESSED_COUNTS$filteredExprMatrix$counts %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'HBCC_DLPFC_Counts.tsv', sep = '\t', row.names=F, quote=F)
COUNT_OBJ = File('HBCC_DLPFC_Counts.tsv', name = 'Counts (filtered raw)', parentId = CODE$properties$id)
annotations(COUNT_OBJ) = annotations(CODE)
annotations(COUNT_OBJ)$dataSubType = 'filteredCounts'
COUNT_OBJ = synStore(COUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store filtered counts
NEW.COUNTS %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'HBCC_DLPFC_nCounts.tsv', sep = '\t', row.names=F, quote=F)
NCOUNT_OBJ = File('HBCC_DLPFC_nCounts.tsv', name = 'Counts (estimated)', parentId = CODE$properties$id)
annotations(NCOUNT_OBJ) = annotations(CODE)
annotations(NCOUNT_OBJ)$dataSubType = 'estimatedCounts'
NCOUNT_OBJ = synStore(NCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store logCPM
CQN.GENE_EXPRESSION$E %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'HBCC_DLPFC_logCPM.tsv', sep = '\t', row.names=F, quote=F)
LCOUNT_OBJ = File('HBCC_DLPFC_logCPM.tsv', name = 'Counts (filtered logCPM)', parentId = CODE$properties$id)
annotations(LCOUNT_OBJ) = annotations(CODE)
annotations(LCOUNT_OBJ)$dataSubType = 'filteredLCPM'
LCOUNT_OBJ = synStore(LCOUNT_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store cqn offsets
CQN.GENE_EXPRESSION$offset %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'HBCC_DLPFC_offset.tsv', sep = '\t', row.names=F, quote=F)
OFFSET_OBJ = File('HBCC_DLPFC_offset.tsv', name = 'Gene length and GC content offset', parentId = CODE$properties$id)
annotations(OFFSET_OBJ) = annotations(CODE)
annotations(OFFSET_OBJ)$dataSubType = 'offset'
OFFSET_OBJ = synStore(OFFSET_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store design matrix
DM1$design %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'HBCC_DLPFC_Design.tsv', sep = '\t', row.names=F, quote=F)
DM_OBJ = File('HBCC_DLPFC_Design.tsv', name = 'Design Matrix', parentId = CODE$properties$id)
annotations(DM_OBJ) = annotations(CODE)
annotations(DM_OBJ)$dataSubType = 'designMatrix'
DM_OBJ = synStore(DM_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store design matrix
SURR.VAR %>%
  rownameToFirstColumn('SampleID') %>%
  write.table(file = 'HBCC_DLPFC_SurrVar.tsv', sep = '\t', row.names=F, quote=F)
SURR.VAR_OBJ = File('HBCC_DLPFC_SurrVar.tsv', name = 'Surrogate Variables', parentId = CODE$properties$id)
annotations(SURR.VAR_OBJ) = annotations(CODE)
annotations(SURR.VAR_OBJ)$dataSubType = 'surrogateVariable'
SURR.VAR_OBJ = synStore(SURR.VAR_OBJ, activity = synGetActivity(COV_OBJ$properties$id))

# Store residual gene expression for network analysis
RESIDUAL.SVA.GENE_EXPRESSION %>%
  rownameToFirstColumn('ensembl_gene_id') %>%
  write.table(file = 'HBCC_DLPFC_eqtlResidualExpression.tsv', sep = '\t', row.names=F, quote=F)
eEXP_OBJ = File('HBCC_DLPFC_eqtlResidualExpression.tsv', 
                name = 'Normalised, covariates removed residual expression (for eQTL analysis)', 
                parentId = CODE$properties$id)
annotations(eEXP_OBJ) = annotations(CODE)
annotations(eEXP_OBJ)$dataSubType = 'residualGeneExpForNetAnlz'
eEXP_OBJ = synStore(eEXP_OBJ, activity = synGetActivity(COV_OBJ$properties$id))
